### 2020-10-20 submission/manuscript.Rmd
Create Figure S3, rename files

**Removing treatment group effects from community data.** Because treatment effects often affect a sample's diversity and inter-sample variation, I generated null distributions for each study by randomizing the number of times each ASV was observed in each sample such that the total number of sequences in each sample and the total number of times each ASV was observed across all samples in the study was the same as was originally observed. This effectively made every community in a study a statistical sample of the study-wide composite community distribution. For example, after this procedure, the 490 samples from the human dataset would be expected to have the same number of ASVs and diversity and one would not expect to find treatment-based effects between the samples. Because of the risk of bias if only one representation of the null distribution was generated, I generated 100 randomized datasets for each study. The same trends between removing rare ASVs and the number of ASVs, sample diversity, and information loss that were identified using the observed community community distribution data were also identified with the data from the null distribution (**Figure S2**). The null distribution data were used in the remainder of the study.

>>>>

**Removing treatment group effects from community data.** Because treatment effects often affect a sample's diversity and inter-sample variation, I generated null distributions for each study by randomizing the number of times each ASV was observed in each sample such that the total number of sequences in each sample and the total number of times each ASV was observed across all samples in the study was the same as was originally observed. This effectively made every community in a study a statistical sample of the study-wide composite community distribution. For example, after this procedure, the 490 samples from the human dataset would be expected to have the same number of ASVs and diversity and one would not expect to find treatment-based effects between the samples. Because of the risk of bias if only one representation of the null distribution was generated, I generated 100 randomized datasets for each study. The trends between removing rare ASVs and the number of ASVs or OTUs, sample diversity, and information loss that were identified using the observed community community distribution data were also identified with the data from the null distribution; however, the losses were larger when using the null distribution data (**Figure S3**). The null distribution data were used in the remainder of the study to minimize the risk of bias.
